Fig2: Candidate genes

### 2020-04-29 analysis/figure-2.Rmd
better table

## table 1 summary candidate genes
table1 <- left_join(candidateDEGS, parentalcaregenes) %>%
  select(gene, control_bldg:n5_n9, parentalcare, parentalbehavior, NCBI) %>%
  mutate(parentalcare = if_else(is.na(parentalcare), " ", "X"),
         parentalbehavior = if_else(is.na(parentalbehavior), " ", "X")) %>%
  rename("Literature" = "parentalcare", "GO" =  "parentalbehavior")
table1$numDEGs <- rowSums(is.na(table1)) # count NAs to know how many are NS
table1 <- table1 %>% 
  mutate(sig = ifelse(numDEGs == 6, "NS", "DEG")) %>% 
  arrange(sig, gene)  %>%  select(-sig, -numDEGs)
table1[is.na(table1)] <- " " # replace NA with blank space so it's pretty
head(table1)

>>>>

## table 1 summary candidate genes
table1 <- left_join(candidateDEGS, parentalcaregenes) %>%
  select(gene, control_bldg:n5_n9, parentalcare, parentalbehavior, NCBI) %>%
  mutate(parentalcare = if_else(is.na(parentalcare), " ", "X"),
         parentalbehavior = if_else(is.na(parentalbehavior), " ", "X")) %>%
  rename("Literature" = "parentalcare", "GO" =  "parentalbehavior")
table1$numDEGs <- rowSums(is.na(table1)) # count NAs to know how many are NS

table1 <- table1 %>% 
  mutate(sig = ifelse(numDEGs == 6, "NS", "DEG")) %>% 
  arrange(gene)  %>%  select(-sig, -numDEGs)
table1[is.na(table1)] <- " " # replace NA with blank space so it's pretty
head(table1)
